\todo{Something} presents OpenAdcess

### 2017-02-28 digital-library.tex
Outsourced captchas

\subsection{Outsourced Captias}
\todo{Force free-tier users to solve a captia, but the captia is actually from
  another site and we collect money from spammers to solve these captias ala
mechanical turk}

>>>>

\subsection{Outsourced Captchas}
When a user requests a paper download, they will be required to submit a
captcha.
While many websites use captcha to prevent automated abuse, we see an
opportunity to profit.
We provide an API to botnets with which they may submit captchas to be
displayed to users attempting to download files.
Their responses to these captchas are sent back to the botnet thus allowing the
botnet to proceed with whatever attack the captcha was preventing.
We believe we can sell this human captcha solving service for a few cents per
captcha.

Additionally, users will not question the presence of captchas on the digital
library as they have already been conditioned to fill captchas for all sorts of
free services.
As such, we do not believe that our user base will know that the ACM is
slinging captcha solutions on the side.

### 2017-02-28 paper-sponsorships.tex
Outsourced captchas

\section{Paper Sponsorships}

>>>>

\section{Paper Sponsorships}
Reach the largest holistic-minded audience in the entire northeastern United
States with an ad in the next ACM edition.
Our public mostly devoid of energy vampires and is therefore suitable for
empath advertisers.
Where IEEE uses Western proof verification techniques, our broad minded
audience validates mathematical claims in an intuitive holistic manner and will
bring that same spirit into evaluating the claims of your advertisements.
Our readers will engage with your brand through meditation and other
surprises.
